Real-time resolution of short-read assembly graph using ONT long reads

### 2020-10-25 paper_clean.tex
Begin minor revision

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

@@

Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.  However, \npscarf{} ignores the rich connectivity information in the short read assembly graph, and as a result is relatively prone to mis-assembly compared to alternative methods.
%The strategy proved to be
%a time- and cost- effective methodology where practitioners need to generate only sufficient data for completing 
%a draft genome.

@@

%\begin{figure}[!hpt]
%\centering
%\subfloat[Merging bridges]{
%    \label{figure:npgraph_merge}
%	\includegraphics[width=.48\textwidth]{images/bridge_merging.pdf}
%}
%\hfill
%\subfloat[Knot untangled]{
%    \label{figure:npgraph_untangle}
%	\includegraphics[width=.48\textwidth]{images/knot.pdf}
%}
%\caption{Graph resolving algorithm. \ref{figure:npgraph_merge} the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors. \ref{figure:npgraph_untangle} A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
%\label{figure:npgraph_pipeline}
%\end{figure}

\begin{figure}[!hpt]
\centering
\includegraphics[width=\textwidth]{images/Fig1.eps}
\caption{Graph resolving algorithm. (a) the bridges suggested by long reads are merged progressively with dynamic programming to find the best path connecting 2 anchors. (b) A knot (repetitive contig) is unwound following the best path (highlighted in purple) leading to the graph simplification.}
\label{figure:npgraph_pipeline}
\end{figure}

@@

\begin{figure}[!hpt]
\centering
\includegraphics[width=\textwidth]{images/Fig2.eps}
\caption{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}). The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}). From the Dashboard there are 5 components as follow: \textbf{1} the assembly graph input field; \textbf{2} the long reads input field; \textbf{3} the aligner settings field; \textbf{4} control buttons (start/stop) to monitor the real-time scaffolding process; \textbf{5} the statistics plots for the assembly result.}
\label{figure:npgraph_gui}
\end{figure}

@@

The first step in our binning procedure is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
 define a customised metric which is simple and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage. 
%The rationale is to approximate a coverage value of an extremely long contig (which can be split into more than 10,000 \emph{k-mers}) with a sampled mean of a Poisson distribution (of \emph{k-mers} count). 
The metric is then determined by a distance function of two Poisson distributions based on Kullback-Leibler divergence (or relative entropy) between the Poisson distribution representing each contig\cite{Kullback1951information}.

@@

% After identifying the bins, we implemented a graph traversal to assign more unique nodes to them, given the graph topology as well as statistics calculated by length and coverage of each contigs. 
Independent from the contigs clustering in the pre-processing step, additional evidence of nodes' uniqueness can be acquired using the long reads during the assembly process. Given enough data, the multiplicity of an ambiguous node can be determined based on the set of all bridges rooted from itself.
On the other hand, external binning tools such as MetaBAT~\cite{Kang2015metabat}, maxbin~\cite{Wu2014maxbin} can be employed in \npgraph{} as well.
%If external binning algorithm is employed, the resulting output must be converted into a text file that specifies the corresponding bin of every contigs, just like output from MetaBAT. By that, each line of the file would be:
%$
%\mathtt{<contig\_ID>} \; ~ \mathtt{<bin\_ID>}
%$
%where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
\subsubsection*{Multiplicity estimation}
Now bins of the main unique contigs had been identified, however, they only make up a certain proportion of the contigs set. From here, we need to assign bin membership and multiplicity for all other nodes of the graph, especially the repetitive ones. To do so, we relied on the graph's topology and the estimated read coverage of initial contigs from SPAdes.
Given all contigs' coverage values as nodes' weight, we need to estimate those of edges and in return, using them to re-estimate the coverage for repetitive nodes if necessary. After this process, we will have a graph with optimized weighted components that would suggest their multiplicities more exactly. Basically the computation is described as in following steps:

@@

% \begin{figure}[!hpt]
% \centering
% \includegraphics[width=.8\textwidth]{images/bridge_merging.pdf}
% \caption[Example of bridge merging progressively]{Bridge merging progressively in real-time. Sequencing long reads induce alignments to the contigs where new bridges are created respectively. Bridges sharing same anchors can be merged together to form the ultimate, more comprehensive bridge (with more step nodes and better approximation of spans between them).}
% \label{figure:npgraph_merging}
% \end{figure}

@@

\begin{algorithm}[!hpt]
\DontPrintSemicolon
\KwData{Assembly graph $G\{V,E\}$}
\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_n}$ that maximize the likelihood of the step list.}
\SetKwFunction{BinaryBridging}{BinaryBridging} 
\SetKwProg{Fn}{Function}{:}{}
\Fn{\BinaryBridging{B}}{
\tcc{search for the contig with maximum score from the step list (two ends excluded)}
$m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
\tcc{if there is no step in-between, run Algorithm~\ref{algo:findpath} and return the result}
\If{$M.size() \equiv 2$}{ 
	\Return{$\mathtt{DFS}(B.start(),B.end().B.distance())$}
}
\tcc{divide the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
$BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
$BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
\tcc{Return the join of running recursive function on two sub-bridges}
\Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
}
\caption{Recursive binary bridging to connect 2 anchor nodes.}
\label{algo:binsearch}
\end{algorithm}

@@

Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover. During the traversal, a variable $d$ is updated as an estimation for the distance to the target. A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21). 
A threshold for the traversing depth is set (150) to ignore too complicated and time-consuming path searching.

Note that the $length()$ functions for node and edge are totally different. While the former returns the length of the sequence represented by the node, \IE{} contig from short-read assembly, the latter is usually negative because an edge models a link between two nodes, which is normally an overlap (except for composite edges). For example, in a \emph{k-mers} SPAdes assembly graph, the value of an edge is $-k+1$.

@@

\begin{figure}[!hpt]
\centering
 \includegraphics[width=\textwidth]{images/Fig4.eps}
\caption{Assembly graph of \emph{Shigella~dysenteriae} Sd197 synthetic data being resolved by \npgraph{} and displayed on the GUI Graph View. The \spades{} assembly graph contains 2186 nodes and 3061 edges, after the assembly shows 2 circular paths representing the chromosome and one plasmid.}
\label{figure:npgraph_graphview}
\end{figure}

@@

\begin{figure}[!hpt]
\centering
\includegraphics[width=.6\textwidth]{images/Fig5.eps}
\caption{Example of graph decomposition into longest straight paths. Branching edges are masked out (faded) leaving only straight paths (bold) to report. There would be 3 contigs extracted by traversing along the straight paths here.}
\label{figure:npgraph_decompose}
\end{figure}

@@

\subsection*{Hybrid assembly for real data sets}
%The complicated graph topology from \emph{S.~dysenteriae} simulation is not common in real-life application.  %%CAN WE SUPPORT BETTER
%Also, considering the potential for performance bias of \unicycler{} on its own test sets, we collected real-life sample for further comparison of \unicycler and \npgraph.
A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (
Table~\ref{tab:npgraph_real}) 
%shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.

@@

In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in S1 Fig. This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly. This was caused by the inconsistency of a fragment's direction on the final output contigs. Comparison to a reference 
 genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (S2 Fig.). However, we cannot at this stage rule out genuine structural variation between the two samples .

@@

%\begin{figure}[!hbt]
%\centering
%\subfloat[\emph{Citrobacter~freundii} CAV1374]{
%	\includegraphics[width=.45\textwidth]{images/rt_cf1374.png}
%}
%\hfill
%\subfloat[\emph{Escherichia~coli} K12 MG1655]{
%	\includegraphics[width=.45\textwidth]{images/rt_eck12.png}
%}
%\\
%\subfloat[\emph{Klebsiella} 30660 NJST258]{
%	\includegraphics[width=.45\textwidth]{images/rt_kp30660.png}
%}
%\hfill
%\subfloat[\emph{Klebsiella} NTUH K2044]{
%	\includegraphics[width=.45\textwidth]{images/rt_kpntuh.png}
%}
%\caption[Real-time assembly by \npscarf{} and \npgraph{}]{N50 statistics of real-time assembly by \npscarf{} and \npgraph{}.}
%\label{F:npgraph_rt}
%\end{figure}

\begin{figure}[!hbt]
\centering
\includegraphics[width=\textwidth]{images/Fig3.eps}
\caption{N50 statistics of real-time assembly by \npscarf{} and \npgraph{} for 4 bacterial samples.}
\label{F:npgraph_rt}
\end{figure}

@@

The challenge in adapting graph-based  approaches into streaming algorithm comes mainly from building a progressive implementation for path-finding and graph reducing module . 
To achieve this, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.
%The method is implemented in \npgraph{}, a user-friendly tool with GUI that can traverse the assembly graph and bridge its components in real-time while the  nanopore sequencing process is still running.

By testing with synthetic and real data, we have shown that \npgraph{} can generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}, while also providing the ability to build and visualise the assembly in real-time. 
%Furthermore, similar to \npscarf{}, it has the advantage in term of supporting real-time assembly.
%The next section will address this utility and the interactive GUI bundled in \npgraph{}.

%Particularly, for the first time, we employ a pipeline in an attempt to complete metagenomics assembly in real-time. 
%We aim to develop a simple approach on top of \npgraph{} to adapt with metagenomics while minimizing additional processing steps. In fact, only one more step for population binning is needed to make \npgraph{} functions on genomes of a mock community.
%Despite a rather straightforward methodology, the pipeline has shown consecutively enhanced assembly from the fragmented short-read DBG graph

\section*{Conclusion}  %%COMMENT_LC seems repetitive here
%npgraph: how important hybrid assembly
Due to the limits of current sequencing technology, application of hybrid methods should remain a common practice in whole genome assembly for the near future.
On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield and cost. Beside, the real-time property of this technology has not been sufficiently exploited to match its potential benefits.
\npscarf{} had been introduced initially to address these issues, however, the accuracy of the assembly output was affected by its greedy alignment-based scaffolding approach.
Here we present \npgraph{}, a streaming hybrid assembly method working on the DBG assembly graph that is able to finish short-read assembly in real-time while minimizing the errors and mis-assemblies drastically.

@@

%For more information, see \nameref{S1_Appendix}.

\section*{Supporting information}
\renewcommand{\figurename}{Supporting Figure}
\renewcommand{\tablename}{Supporting Table}
\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig} Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}.

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS1.eps}
 \caption{Dotplot generated by MUMmer for assembly results of \unicycler{} versus \npgraph{}. Structural agreements between two methods were found in (a)~\emph{C.freundii} and (b)~\emph{K.oxytoca} assembly contigs. On the other hand, for (c)~\emph{E.cloacae} sample, there was a disagreement detected between 2 largest contigs given by two assembly algorithms.}
\end{figure}

\paragraph*{S2 Fig.}
\label{S2_Fig} Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\unicycler{} and (b)~\npgraph{}

\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{images/FigS2.eps}
 \caption{Alignments of an \emph{Enterobacter~cloacae} reference genome to assembly sequences generated by  (a)~\npgraph{} and (b)~\unicycler{}. The former suggests a structural variant, the latter is virtually an 1-to-1 mapping.}
\end{figure}

\clearpage
\paragraph*{S1 Table.}
\label{S1_Table}
Benchmarking different methods using \lrscaf{}, \npscarf{}, \npgraph{}, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.

\makeatletter

\newlength\oriarrayrulewidth  
\newcount\orilowpenalty
\newcommand\nobreakmidrule{%
 \noalign{\global\oriarrayrulewidth\arrayrulewidth\relax
          \global\orilowpenalty\@lowpenalty\relax  
          \global\@lowpenalty=\numexpr-10000\relax%
          \global\arrayrulewidth\lightrulewidth\relax}
 \hline
 \noalign{\global\@lowpenalty=\orilowpenalty\relax%
          \global\arrayrulewidth\oriarrayrulewidth\relax}}

\makeatother
\setlength{\LTleft}{-1in}
\setcounter{table}{0}

\begin{longtable}[!hpt]{llcrrrrr}
%\caption{Benchmarking \npgraph{} against \npscarf{} versions, $\mathtt{hybridSPAdes}$ and \unicycler{} hybrid assembler with the synthetic data set.}
%\label{supp_tab:synthetic_benchmark}\\
\toprule
    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
    \hline  
\endfirsthead
\multicolumn{8}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
    &       & Assembly &  & N50  & Mis- &  Mismatch & Indel \\
    & Method & size (bp) & \#Contigs  & (bp) & assemblies & (per $100$Kbp) & (per $100$Kbp) \\
\hline
\endhead
\hline \multicolumn{8}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot

\rowcolor{Gray}
\multicolumn{8}{l}{random sequences no repeats} \\* %
\nobreakmidrule
\rowcolor{Gray}
& LRScaf & - & - & - & - & - & - \\*
\rowcolor{Gray}
& npScarf &  4110000 &  3  &  4000000  &  0  & 0.00  & 0.00\\*
\rowcolor{Gray}
& npScarf\_wag & 4109516  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
\rowcolor{Gray}
& npGraph-bwa & 4110000  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
\rowcolor{Gray}
& npGraph-mm2 & 4110000  &  3  &  4000000  &  0  & 0.00  & 0.00\\*
\rowcolor{Gray}
& hybridSPAdes & 4110231  &  3  & 4000077   &  0  & 0.00  &  0.07\\*
\rowcolor{Gray}
& Unicycler & 4110000  &  3  &  4000000  &  0  & 0.00  &  0.00\\
\hline
\multicolumn{8}{l}{random sequences some repeats} \\* %
\nobreakmidrule
& LRScaf & 4113104 & 6 & 4002298 & 0 & 0.00 & 0.00\\*
& npScarf & 4110940  &  3  &  4002715  &  0  &  0.00 &  0.66\\*
& npScarf\_wag & 4437094  &  7 &  2795129  &  0  &  0.00 &  1.07\\*
& npGraph-bwa & 4110000  &  3  &  4000000  &  0 &  0.00 &  0.00\\*
& npGraph-mm2 &  4110000 &  3  &   4000000 & 0  & 0.00  &  0.00\\*
& hybridSPAdes & 4107566  &  3  &  3999364  &  0  & 0.02  & 0.02\\*
& Unicycler &  4110000 &  3 & 4000000  &  0 & 0.00  &  0.00\\
\hline
\rowcolor{Gray}
\multicolumn{8}{l}{random sequences many repeats} \\* %
\nobreakmidrule
\rowcolor{Gray}
& LRScaf & 4119020 & 12 & 4002117 & 0 & 0.03 & 0.79\\* 
\rowcolor{Gray}
& npScarf &  4316934 &  8  &  3963485  &  24  & 11.55  & 34.54\\*
\rowcolor{Gray}
& npScarf\_wag &  5215965 &  16  &  1515563  &  37  & 0.32  & 7.22\\*
\rowcolor{Gray}
& npGraph-bwa & 4110000  &  3  &  4000000  &  0  &  0.32 & 0.15\\*
\rowcolor{Gray}
& npGraph-mm2 &  4110000 &  3  &  4000000  &  0  & 0.32  & 0.15\\*
\rowcolor{Gray}
& hybridSPAdes & 4108190  &  3  &  3999621  &  0  &  0.68 &  0.15\\*
\rowcolor{Gray}
& Unicycler & 4110000  &  3  &  4000000  &  0  &  0.32  & 0.15  \\
\hline
% \pagebreak
% \toprule
\multicolumn{8}{l}{\emph{Acinetobacter} A1} \\* %
\nobreakmidrule
& LRScaf & 3896799 & 4 & 3886381 & 0 & 0.47 & 0.36\\*
& npScarf & 3912299  &  3  &  3870269  &  4  & 4.74  & 13.02 \\*
& npScarf\_wag & 3945166  &  3  &  3906368  &  1  & 7.00  & 14.02 \\*
& npGraph-bwa & 3918374  &  2  &  3909643  &  0 & 16.34  & 0.61 \\*
& npGraph-mm2 & 3885898  &  2  &  3877167  & 1 & 18.05  & 1.03 \\*
& hybridSPAdes &  3929948 &  53  &  3353679  &  0  & 35.48  & 3.22\\*
& Unicycler & 3917745  &  2 & 3909014  & 0  & 2.50  &  0.13\\
\hline
\rowcolor{Gray}
\multicolumn{8}{l}{\emph{Acinetobacter} AB30} \\* %
\nobreakmidrule
\rowcolor{Gray}
& LRScaf & 4367657 & 27 & 1035967 & 13 & 30.11 & 1.42\\* 
\rowcolor{Gray}
& npScarf & 4512464  &  7  &  4304628  &  35  & 57.95  & 72.87\\*
\rowcolor{Gray}
& npScarf\_wag & 5315235  &  13  &  1267710  &  136  &  73.55 & 8.15\\*
\rowcolor{Gray}
& npGraph-bwa & 4335342  &  2  &  4148952  &  1  & 16.93  & 1.45\\*
\rowcolor{Gray}
& npGraph-mm2 & 4335790  &  1  &  4335790  & 0   &  6.97 & 0.25\\*
\rowcolor{Gray}
& hybridSPAdes & 4337369  &  3  &  2701005  &  0  &  12.80 &  1.39\\*
\rowcolor{Gray}
& Unicycler &  4333041 &  1  &  4333041  &  1  &  6.42 &  0.53\\
\hline
\multicolumn{8}{l}{\ec{} K12 MG1655} \\* %
\nobreakmidrule
& LRScaf & 4732001 & 16 & 692794 & 7 & 3.42 & 0.58\\*
& npScarf & 4649902  &  2  &  4641702  &  4  & 14.94  & 34.35 \\*
& npScarf\_wag &  4687952 &  3  &  4641732  &  0  & 6.55  &  1.96\\*
& npGraph-bwa & 4641743  &  1  &  4641743  & 0  &  4.50 & 0.43 \\*
& npGraph-mm2 & 4641820  &  1  &  4641820  &  0 &  3.88 & 0.26 \\*
& hybridSPAdes &  4644555 &  1  &  4641036  &  0  & 0.62  & 0.09\\*
& Unicycler & 4641650  &  1 &  4641650 &  0 & 3.43  & 0.26 \\
\hline
\rowcolor{Gray}
\multicolumn{8}{l}{\ec{} O25b H4-ST131} \\* %
\nobreakmidrule
\rowcolor{Gray}
& LRScaf & 5410854 & 21 & 910949 & 9 & 13.70 & 0.87\\*
\rowcolor{Gray}
& npScarf &  5245913 &  3  &  5095571  &  7  &  7.05 & 18.81\\*
\rowcolor{Gray}
& npScarf\_wag & 5292700  &  3  &  3469617  &  9  &  9.03 & 1.55\\*
\rowcolor{Gray}
& npGraph-bwa & 5237821  &  7  &  4049493  &  1  &  3.38 & 0.31\\*
\rowcolor{Gray}
& npGraph-mm2 &  5249799 &  3  &  5110117  &  0  &  2.40 & 0.15\\*
\rowcolor{Gray}
& hybridSPAdes & 5252762  &  8  &  4258948  &  2  &  5.43 &  0.57\\*
\rowcolor{Gray}
& Unicycler & 5249442  &  3  &  5109760  &  0  & 4.02 & 0.27 \\
\hline
% \pagebreak
% \toprule
\multicolumn{8}{l}{\emph{Klebsiella} 30660 NJST258 1} \\* %
\nobreakmidrule
& LRScaf & 5512518 & 20 & 777919 & 26 & 3.52 & 0.38\\*
& npScarf & 5559772  &  7  &  5259053  &  4  & 17.18  & 13.48\\*
& npScarf\_wag & 5613780  &  7  &  5268535  &  6  & 1.59  & 1.92\\*
& npGraph-bwa & 5534843  &  8  &  5263229  &  0  & 3.15  & 0.76\\*
& npGraph-mm2 & 5534878  &  8  &  5263264  &  0  & 2.75  & 0.74\\*
& hybridSPAdes &  5545668 & 8   &  5545668  &  2  & 4.95  & 0.09 \\*
& Unicycler & 5537860  &  9  &  5263196  &  0  & 1.34  & 0.51 \\
\hline
\rowcolor{Gray}
\multicolumn{8}{l}{\emph{Klebsiella} MGH 78578} \\* %
\nobreakmidrule
\rowcolor{Gray}
& LRScaf & 5823340 & 38 & 559414 & 7 & 5.92 & 1.27\\*
\rowcolor{Gray}
& npScarf &  5729304 &  5  &  5316429  &  12  & 14.90  & 20.27\\*
\rowcolor{Gray}
& npScarf\_wag & 5754443  &  5  &  3026286  &  16  &  8.17 & 2.56\\*
\rowcolor{Gray}
& npGraph-bwa &  5695801 &  7  &  5311745  &  1  & 12.65  & 1.25\\*
\rowcolor{Gray}
& npGraph-mm2 & 5696302  &  6  &  5315267  &  0  &  6.06 & 0.44\\*
\rowcolor{Gray}
& hybridSPAdes &  5706470 &  11  &  5315273  &  1  & 3.82  &  0.67\\*
\rowcolor{Gray}
& Unicycler &  5694231 &  14  &  5315096  &  0  & 5.38 &  0.21\\
\hline
\multicolumn{8}{l}{\emph{Klebsiella} NTUH-K2044} \\* %
\nobreakmidrule
& LRScaf & 5470282 & 8 & 2951488 & 9 & 3.04 & 2.62\\*
& npScarf & 5471696  &  2  &  5249198  &  6  & 4.82  &  8.55\\*
& npScarf\_wag & 5530559  &  3  &  5249369  &  2  &  2.25 &  1.35\\*
& npGraph-bwa & 5472629  &  2  &  5248476  & 0  & 2.52  &  0.31\\*
& npGraph-mm2 &  5472655 &  2  &  5248503  &  0 &  1.21 &  0.26\\*
& hybridSPAdes & 5473572  &  2  &  5248894  &  0  &  0.44 & 0.15\\*
& Unicycler & 5472697  & 2  & 5248545  &  0 & 2.41  &  0.35\\
\hline
\rowcolor{Gray}
\multicolumn{8}{l}{\emph{Mycobacterium tuberculosis} H37Rv} \\* %
\nobreakmidrule
\rowcolor{Gray}
& LRScaf & 4260869 & 12 & 3215170 & 8 & 6.69 & 2.27\\*
\rowcolor{Gray}
& npScarf &  4498245 &  4  & 4402238   &  8  & 5.15  & 2.68\\*
\rowcolor{Gray}
& npScarf\_wag &  4506056 &  4  &  4410942  &  3  & 6.81  & 2.59\\*
\rowcolor{Gray}
& npGraph-bwa & 4411406  &  1  &  4411406  &  0  & 1.88  & 0.43\\*
\rowcolor{Gray}
& npGraph-mm2 & 4411532  & 1   &  4411532  &  0  & 0.68  & 0.00\\*
\rowcolor{Gray}
& hybridSPAdes & 4413942  &  1  &  4410519  &  0  &  0.75 &  0.11\\*
\rowcolor{Gray}
& Unicycler & 4411538  &  1  &  4411538  &  0  &  2.22 &  0.34\\
\hline
% \pagebreak
% \toprule
\multicolumn{8}{l}{\emph{Saccharomyces cerevisiae} S288c} \\* %
\nobreakmidrule
& LRScaf & 12486884 & 214 & 254587 & 27 & 16.45 & 1.97\\*
& npScarf &  11986800 &  24  &  796769  &  51  &  62.12 & 21.46 \\*

>>>>

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Hybrid genome assembly algorithms combine high accuracy short reads with error-prone long reads with the goal of generating highly contiguous assemblies with low error rates.  
Short read sequence data is relatively inexpensive in comparison to long-read sequence data, and, moreover short-read sequence data has already been collected for many bacterial species, thus motivating development of methods wh
ich are frugal with respect to acquisition of long-read sequence data.   One of the attractive features of the Oxford Nanopore Technology’s sequencers is that they generate sequence data in real-time, and in principle sequencing can be stopped once enough data is acquired.   However, there is only one previous attempt for greedy genome scaffolding of contigs in real-time, which was prone to assembly errors.   
In this paper we describe a new tool – \npgraph{} – which resolves the assembly graph in real-time as sequence is generated; coupled with assembly visualisation showing assembly graph resolution in real-time.  We show that \npgraph{} generates completed bacterial assemblies which are as accurate as state-of-the-art batch hybrid assembly pipelines, and also provides substantial computational speed-up.

@@

Previously, we developed \npscarf{}~\cite{Cao2017scaffolding} an algorithm to scaffold a draft assembly from Illumina sequencing simultaneously with ONT sequencing.  However, \npscarf{} ignores the rich connectivity information in the short read assembly graph, and as a result is relatively prone to mis-assembly compared to alternative methods.

@@

@@

@@

The first step in our binning procedure is to cluster the big anchors (longer than $10$Kbp and in/out degree less than 2) based on their \emph{kmer} coverage.
To achieve this, we applied DBSCAN clustering algorithm \cite{Ester96adensity-based}, which utilises a customised metric function to map contigs into a one-dimensional space.  In order to 
 define a customised metric which is simple and fast to calculate, we assumed that a single long contig itself consists of a Poisson distribution of \emph{k-mers} count with the mean approximated by the contig's coverage. 
The metric is then determined by a distance function of two Poisson distributions based on Kullback-Leibler divergence (or relative entropy) between the Poisson distribution representing each contig\cite{Kullback1951information}.

@@

Independent from the contigs clustering in the pre-processing step, additional evidence of nodes' uniqueness can be acquired using the long reads during the assembly process. Given enough data, the multiplicity of an ambiguous node can be determined based on the set of all bridges rooted from itself.
On the other hand, external binning tools such as MetaBAT~\cite{Kang2015metabat}, maxbin~\cite{Wu2014maxbin} can be employed in \npgraph{} as well.

\subsubsection*{Multiplicity estimation}
Now bins of the main unique contigs had been identified, however, they only make up a certain proportion of the contigs set. From here, we need to assign bin membership and multiplicity for all other nodes of the graph, especially the repetitive ones. To do so, we relied on the graph's topology and the estimated read coverage of initial contigs from SPAdes.
Given all contigs' coverage values as nodes' weight, we need to estimate those of edges and in return, using them to re-estimate the coverage for repetitive nodes if necessary. After this process, we will have a graph with optimized weighted components that would suggest their multiplicities more exactly. Basically the computation is described as in following steps:

@@

@@

\begin{algorithm}[!hpt]
\DontPrintSemicolon
\KwData{Assembly graph $G\{V,E\}$}
\KwIn{Brigde $B:\lbrace\overrightarrow{v_0}, ...\overrightarrow{v_k}, ...,\overrightarrow{v_n}\rbrace$ with $\overrightarrow{v_0}$ and $\overrightarrow{v_n}$ are two anchors, $\{\overrightarrow{v_k}\}, k=1\ldots(n-1)$ are steps in-between}
\KwOut{Set of candidate paths connecting $\overrightarrow{v_0}$ to $\overrightarrow{v_n}$ that maximize the likelihood of the step list.}
\SetKwFunction{BinaryBridging}{BinaryBridging} 
\SetKwProg{Fn}{Function}{:}{}
\Fn{\BinaryBridging{B}}{
\tcc{search for the contig with maximum score from the step list (two ends excluded)}
$m$:=$\argmax_k(\overrightarrow{v_k}.score())$ \;
\tcc{if there is no step in-between, run Algorithm~\ref{algo:findpath} and return the result}
\If{$M.size() \equiv 2$}{ 
	\Return{$\mathtt{DFS}(B.start(),B.end().B.distance())$}
}
\tcc{break the original bridge $B$ into 2 bridges by $v_m$: $BL$ and $BR$}
$BL$:=$\lbrace B.start(), ...,\overrightarrow{v_m}\rbrace$ \;
$BR$:=$\lbrace \overrightarrow{v_m}, ...,B.end()\rbrace$ \;
\tcc{recursively invoke the procedure and join the results together}
\Return{$\BinaryBridging(BL)\Join\BinaryBridging(BR)$} 
}
\caption{Recursive binary bridging to connect 2 anchor nodes.}
\label{algo:binsearch}
\end{algorithm}

@@

Basically, the algorithm keeps track of a stack that contains sets of candidate edges to discover. During the traversal, a variable $d$ is updated as an estimation for the distance to the target. A hit is reported if the target node is reached with a reasonable distance \IE{} close to zero, within a given tolerance (line 21). 
Another threshold for the maximum traversing depth is set and heuristic cut-off can be used to preven exceptional combinatorial explosion when traversing extremely complex graph components.

It worths noting that from the pseudo code in Algorithm~\ref{algo:findpath}, despite of identical name,, procedure $length()$ used for nodes are different than for edges. The former would return the contig length while the latter measure the overlap or distance between a pair of contigs thus can be negative or positive respectively. From De Bruijin graph for instance, all edges have same the length value of $-k$. In \npgraph{}'s algorithm, an edge's length can vary as we allow additional connection types on top of the original \spades{} assembly graph input.

@@

@@

@@

\subsection*{Hybrid assembly for real data sets}
A number of sequencing data sets from \emph{in vitro} bacterial samples~\cite{George2017M14} were used to further explore differences in performance between \npgraph{} and \unicycler{}.
The data included both Illumina paired-end reads and MinION sequencing based-call data for each sample.
Due to the unavailability of reference genomes, there were fewer statistics reported by QUAST for the comparison of the results. 
Instead, we investigated the number of circular sequences and $\mathtt{PlasmidFinder}$ 1.3~\cite{Carattoli2014} mappings to obtain an evaluation on the accuracy and completeness of the assemblies (Table~\ref{tab:npgraph_real}) 
%shows the benchmark results of \npgraph{} (using \minimap{}) against \unicycler{} 
on three data sets of bacterial species \emph{Citrobacter~freundii}, \emph{Enterobacter~cloacae} and \emph{Klebsiella~oxytoca}.

@@

In addition to what is presented in Table~\ref{tab:npgraph_real}, dot plots for the pair-wise alignments between the assembly contigs were generated and can be found in Figure S1. This identified a structural difference between \npgraph{} and \unicycler{} assembly for the \emph{E.~cloacae} CAV1411 genome assembly. This was caused by the inconsistency of a fragment's direction on the final output contigs. Comparison to a reference 
 genome from the same bacteria strain (GenBank ID: CP011581.1~\cite{Potter2016rapid}), demonstrated that contigs generated by \npgraph{} produced consistent alignment, but not those generated by \unicycler{} (Figure S2). However, we cannot at this stage rule out genuine structural variation between the two samples .

@@

@@

The challenge in adapting graph-based  approaches into streaming algorithm comes mainly from building a progressive implementation for path-finding and graph reducing module . 
To achieve this, we apply a modified DFS (depth-first search) mechanism and a dynamic voting algorithm into an on-the-fly graph resolver.

By testing with synthetic and real data, we have shown that \npgraph{} can generate assemblies of comparative quality compared to other powerful batch-mode hybrid assemblers, such as $\mathtt{hybridSPAdes}$ or \unicycler{}, while also providing the ability to build and visualise the assembly in real-time.

\section*{Conclusion}
%npgraph: how important hybrid assembly
Due to the limits of current sequencing technology, application of hybrid methods should remain a common practice in whole genome assembly for the near future.
On the other hand, the ONT platforms are evolving quickly with significant improvement in terms of data accuracy and yield and cost. Beside, the real-time property of this technology has not been sufficiently exploited to match its potential benefits.
\npscarf{} had been introduced initially to address these issues, however, the accuracy of the assembly output was affected by its greedy alignment-based scaffolding approach.
Here we present \npgraph{}, a streaming hybrid assembly method working on the DBG assembly graph that is able to finish short-read assembly in real-time while minimizing the errors and mis-assemblies drastically.

@@
